---
title: "SPAM Detection HW"
author: "Ahmet Emin Saricaoglu"
date: "20 12 2020"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
    number_sections: true
---

```{r, include=FALSE}
## install.packages('rpart')
## install.packages('installr')
## install.packages('rpart.plot')
## install.packages('RColorBrewer')
## install.packages('rattle')
library(RColorBrewer)
library(rattle)
library(rpart.plot)
library(installr)
library(tidyverse)
library(lubridate)
library(tidyr)
library(dplyr)
library(ggplot2)
library(rpart)
```

# Import Dataset

```{r, warning=FALSE, message= FALSE}
setwd("C:/Users/ahmet/Desktop/MEF_BDA/BDA-503/Week_6/HW_Spam_Detection")
spamdata = read.csv(file = 'spam_Data.csv')
head(spamdata)
glimpse(spamdata)
dim(spamdata)
```

# Split to Training and Test Set

Split spam dataset into train and test dataset.
Split ratio = 0.80

```{r, warning=FALSE, message= FALSE}
smp_size <- floor(0.80 * nrow(spamdata))
set.seed(50)
train_ind <- sample(seq_len(nrow(spamdata)), size = smp_size)
train <- spamdata[train_ind, ]
test <- spamdata[-train_ind, ]
```

# Build the Model

Build the model with the training data and show graph.

```{r, warning=FALSE, message= FALSE}
spam_tree <- rpart(class~.,data = train, method = 'class')
fancyRpartPlot(spam_tree)
```

# Explication

```{r, warning=FALSE, message= FALSE}
printcp(spam_tree)
plotcp(spam_tree)
```

# Test Prediction 

We can predict our test dataset.

## Confusion Matrix 
```{r, warning=FALSE, message= FALSE}
predict_unseen <-predict(spam_tree, test, type = 'class')
cm <- table(test$class, predict_unseen)
cm
```
There are 833 true prediction and 88 false prediction.
For 88 false prediction;
  * There are 26 false positive result
  * There are 62 false negative result

## Performance Measurement
```{r, warning=FALSE, message= FALSE}
accuracy_Test <- sum(diag(cm)) / sum(cm)
print(paste('Accuracy for test', accuracy_Test))
```
# Tune the hyper-parameters
```{r, warning=FALSE, message= FALSE}
accuracy_tune <- function(fit) {
    predict_unseen <- predict(spam_tree, test, type = 'class')
    table_mat <- table(test$class, predict_unseen)
    accuracy_Test <- sum(diag(table_mat)) / sum(table_mat)
    accuracy_Test
}

control <- rpart.control(minsplit = 4,
    minbucket = round(5 / 3),
    maxdepth = 3,
    cp = 0)
tune_fit <- rpart(class~., data = train, method = 'class', control = control)

predict_tune<-predict(tune_fit, test, type = 'class')
cm_fit <- table(test$class, predict_tune)
cm_fit
accuracy_test_tune <- sum(diag(cm_fit)) / sum(cm_fit)
print(paste('Accuracy for test', accuracy_test_tune))
```



